An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-29 VLDB2026/main.tex
Update main.tex

	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different recall and QPS.

>>>>

	For all evaluated algorithms, we adopt the parameter settings recommended in the original study and adjust the parameters related to search in order to obtain different Recall and QPS.
